### 2021-07-03 docs/manuscript/manuscript.tex
Add field size to results

The average vertex degree indicates that in general all the network topologies
display high robustness and that they could resist an average of approximately 4
topological mutations without losing their fitness. Additionally, the average
path length indicates that the evolutionary landscape is easily accessible for
most network topologies (Table~\ref{table1}).

>>>>

The average vertex degree indicates that in general, all the network topologies
display high robustness and that they could resist an average of approximately 4
topological mutations without losing their fitness. Additionally, the average
path length indicates that the evolutionary landscape is easily accessible for
most network topologies (Table~\ref{table1}). Although the GRNs in this modelling
framework are robust to changes in its topology, they are sensitive to changes in
the morphogenetic field size, especially when this size is reduced, as only
4.66, 56.82, 56.14 and 41.05 percent of the GRNs had a fitness greater than 0.9
in fields with 10, 20, 40 and 50 cells, respectively (\nameref{S5_Fig}B).
